### 2023-10-17 2.State/gru.tex
changed gru full and no full forms
Change to GRU

\section{\acf{GRU}}
The \ac{GRU} is another type of \ac{RNN}. It is also known to reduce the effect of the vanishing gradient problem. It was first introduced to improve translation techniques \cite{gru}.

@@

  Some times the \cref{eq:gruHidG} can be found in another form (\cref{eq:gruHidG1}). This, however, has no impact on the final results because it is mathematically equivalent.

>>>>

\section{\acs{GRU}}
The \acf{GRU} is another type of \ac{RNN}. It is also known to reduce the effect of the vanishing gradient problem. It was first introduced to improve translation techniques \cite{gru}.

@@

Sometimes the \cref{eq:gruHidG} can be found in another form (\cref{eq:gruHidG1})\cite{gruPyTorch}. This, however, has no impact on the final results, it means the weights are going to be trained differently for the update gate.
